---
title: "Polygon fees"
author: "Manuel Girbal"
date: "2022-07-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(httr)
library(jsonlite)
library(tidyverse)
library(lubridate)
```

## Introduction

A comparison of fees and transactions between Ethereum and Polygon blockchains:


### Methodology
Data was queried from Flipside Crypto's Velocity database, and the SQL code used is shown below: 

```{sql eval=FALSE}
  with matic as (
    select (date(block_timestamp) ||' '|| hour(block_timestamp))::timestamp as matic_date_hour,
           count(*) as matic_transactions,
           avg(tx_fee) as avg_fee_matic
    from polygon.core.fact_transactions
    where date(block_timestamp) >= '2022-07-01'
    group by matic_date_hour
  )
  ,

  eth as (
    select (date(block_timestamp) ||' '|| hour(block_timestamp))::timestamp as eth_date_hour,
           count(*) as eth_transactions,
           avg(tx_fee) as avg_fee_eth
    from ethereum.core.fact_transactions
    where date(block_timestamp) >= '2022-07-01'
    group by eth_date_hour
  )

  select *
  from matic
  left join eth
  on matic.matic_date_hour = eth.eth_date_hour
```

```{r include=FALSE}
options(scipen=999)

data_1 <- GET("https://node-api.flipsidecrypto.com/api/v2/queries/cab5b462-052f-4409-97ab-10e63ab320f9/data/latest")

data_2 <- rawToChar(data_1$content)

data_3 <- as_tibble(fromJSON(data_2, flatten = TRUE))

data_3$MATIC_DATE_HOUR <- as_datetime(data_3$MATIC_DATE_HOUR)


maticprice <- read.csv("matic-usd-max.csv")
ethprice <- read.csv("eth-usd-max.csv")

maticprice <- as_tibble(maticprice) %>%
  mutate(DATES = as_date(snapped_at)) %>% 
  group_by(DATES) %>% 
  mutate(maticprice = round(mean(price),4)) %>% 
  filter(DATES >= '2022-07-01') %>% 
  select(DATES, maticprice)

ethprice <- as_tibble(ethprice) %>%
  mutate(DATES = as_date(snapped_at)) %>% 
  group_by(DATES) %>% 
  mutate(ethprice = round(mean(price),4)) %>% 
  filter(DATES >= '2022-07-01') %>% 
  select(DATES, ethprice)            


#Merging tables:
data_3$DATES <- as_date(data_3$MATIC_DATE_HOUR)

finaldata <- data_3 %>%
  left_join(maticprice, by = "DATES") %>% 
  left_join(ethprice, by = "DATES") %>% 
  mutate(MATIC_USD_FEE = AVG_FEE_MATIC*maticprice,
         ETH_USD_FEE = AVG_FEE_ETH*ethprice) %>% 
  select(DATE_HOUR = MATIC_DATE_HOUR,
         MATIC_TRANSACTIONS,
         AVG_FEE_MATIC,
         MATIC_USD_FEE,
         ETH_TRANSACTIONS,
         AVG_FEE_ETH,
         ETH_USD_FEE
  )
```


### Analysis
From the plot below, we can see fees are significantly smaller in Polygon (red) than in Ethereum (blue):

```{r echo=FALSE, fig.width = 12}
finaldata %>%
  ggplot(aes(DATE_HOUR)) +
  geom_line(aes(y=MATIC_USD_FEE), size=1, color = "#D55E00") +
  geom_line(aes(y=ETH_USD_FEE), size=1, color = "#00AFBB") +
  theme_minimal() +
  labs(title = "Polygon vs Ethereum transaction fees (in USD vaue)",
       y="USD value",
       x="Date")
```

Also, we can see that they are not correlated:

```{r echo=FALSE}
cor.test(finaldata$MATIC_USD_FEE, finaldata$ETH_USD_FEE, method = "pearson")
```


Also, Polygon appears to process more daily transactions:
```{r echo=FALSE, fig.width = 12}
finaldata %>%
  ggplot(aes(DATE_HOUR)) +
  geom_line(aes(y=MATIC_TRANSACTIONS), size=1, color = "#D55E00") +
  geom_line(aes(y=ETH_TRANSACTIONS), size=1, color = "#00AFBB") +
  theme_minimal() +
  labs(title = "Polygon vs Ethereum transactions",
       y="Transactions",
       x="Date")
```

This also is not correlated:

```{r echo=FALSE}
cor.test(finaldata$MATIC_TRANSACTIONS, finaldata$ETH_TRANSACTIONS, method = "pearson")
```


### Conclusion
Polygon processes more transactions than Ethereum and at much lower fees. However, this fees doesn't seem to be correlated between blockchains.


### References
https://flipsidecrypto.xyz/

https://www.coingecko.com/


### Code: 

https://github.com/manuelgirbal/flipside 

