---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(plotly)
library(httr)
library(jsonlite)
library(tidyverse)
library(lubridate)
library(scales)
```

```{r data, include=FALSE}
data <- GET("https://api.flipsidecrypto.com/api/v2/queries/728f6c73-fbbe-4656-a66b-18c45a2a8058/data/latest")
str(data)
data2 <- rawToChar(data$content)
data3 <- as_tibble(fromJSON(data2, flatten = TRUE))
data3[is.na(data3)] = 0
data3$DATES <- as_date(data3$DATES)
```




--Over the past 30/60/90 days and the past year, how much LUNA has been staked per day? What is the staking percentage (LUNA staked/Circulating Supply), and how has it changed over time?

--To get the circulating supply of LUNA over the past 3 months, we selected the total balance of LUNA from addresses that didn't have labels, in order to exclude exchanges and protocol addresses. From this query we understand that this supply ranged from near 350M to a peak of 407M, but now is situated at 367M.
--However, we can also differentiate between two different balance types: staked LUNA and liquid LUNA. Here we can see that the amount of liquid LUNA during this period is almost always over the staked LUNA, which appears to be diminishing each day.



Column {data-width=300}
-----------------------------------------------------------------------

### Chart A

```{r}
renderPlot({
  data3 %>% 
  filter(DATES < "2022-04-30") %>% 
  ggplot(aes(DATES)) +
  geom_line(aes(y = STAKED, colour = "Staked"), size=1) + 
  geom_line(aes(y = LIQUID, colour = "Liquid"), size=1) +
  theme_minimal() +
  scale_x_date(date_breaks = "1 month", date_labels = "%b-%Y") +
  scale_y_continuous(name = "LUNA Circulating Supply", labels = comma) +
  ggtitle("Staked & Liquid LUNA over time")
})
```

### Chart B

```{r}
data3 %>% 
  filter(DATES < "2022-04-30") %>% 
  ggplot(aes(DATES, STAKED_OVER_CIRCULATING)) +
  geom_line(size=1, color = "darkblue") + 
  theme_minimal() +
  scale_x_date(date_breaks = "1 month", date_labels = "%b-%Y") +
  scale_y_continuous(name = "% of LUNA Staked", labels = comma, limits = c(40,80)) +
  ggtitle("LUNA staked as % of total circulating supply")
```

