---
title: "Terra votes"
author: "Manuel Girbal"
date: "17/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(httr)
library(jsonlite)
library(tidyverse)
```

## Introduction

In this work I'll try to answer one question: how much voting power (measured in LUNA) was used to vote 'YES' for governance proposals in the Terra ecosystem?
In doing so, I'll differentiate validators vs regular wallets.


### Methodology
Data was queried from Flipside Crypto's Velocity database, and the SQL code used is shown below. The result of this chunk is a dataset containing both average voting power and number of addresses that voted yes in each proposal, taking into account which addresses are related to Terra validators and which to regular users:

```{sql eval=FALSE}
select proposal_id::number as id,
       case
          when voter in (select address from terra.labels where label_subtype = 'validator') then 'validator'
          else 'regular'
       end as validator_vs_regular,
       count(voter) as n,   
       avg(voting_power) as mean_voting_power_YES
from terra.gov_vote
where option = 'VOTE_OPTION_YES'
group by proposal_id, validator_vs_regular
```

```{r include=FALSE}
data <- GET("https://api.flipsidecrypto.com/api/v2/queries/ddc05329-2885-464a-ae3a-d6433fd528da/data/latest")
data2 <- rawToChar(data$content)
data3 <- fromJSON(data2, flatten = TRUE)
data3 <- as_tibble(
  data3 %>% 
  mutate(ID = as.factor(ID))
  )
```


### Analysis
First we will see how many addresses voted yes per proposal, and how many belong to validators vs regular users:

```{r echo=FALSE}
data3 %>% 
  ggplot(aes(x = ID, y = N)) +
  geom_point(aes(color = VALIDATOR_VS_REGULAR)) +
  scale_y_continuous(labels = scales::comma, limits = c(0, 4000)) +
  theme(legend.position="bottom",
        axis.text.x = element_text(size=7))
```

From this plot we can observe that validators addresses that vote yes tend to be between 5 and 100, while individual user addresses range mostly from 250 to 3500. 
It all depends on the issue at stake, so taking into account which topic was discussed and voted in each proposal might be helpful to understand participation.

As regards to the average voting power used in each proposal:

```{r echo=FALSE}
data3 %>% 
  ggplot(aes(x = ID, y = MEAN_VOTING_POWER_YES)) +
  geom_point(aes(color = VALIDATOR_VS_REGULAR)) +
  scale_y_continuous(labels = scales::comma, limits = c(0, 600000)) +
  theme(legend.position="bottom",
        axis.text.x = element_text(size=7))
```



### Conclusion
.


### References
https://flipsidecrypto.xyz/

https://docs.terra.money/docs/develop/module-specifications/spec-governance.html

https://docs.terra.money/docs/full-node/manage-a-terra-validator/faq.html



Code used for this publication: https://github.com/manuelgirbal/flipside 