---
title: "Lido HODL or Sell?"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    source_code: https://github.com/manuelgirbal/flipside/tree/main/06.2022%20-%20Lido%20HOLD%20or%20Sell
runtime: shiny
---
<style>
body {
text-align: justify}
</style>

```{r setup, include=FALSE}
library(flexdashboard)
library(httr)
library(jsonlite)
library(tidyverse)
library(lubridate)
library(shiny)
library(plotly)
library(DT)
library(rsconnect)
```

```{r data, include=FALSE}


```


### Introduction

Identify accounts that have staked ETH with Lido when the price of ETH was much higher or much lower than it is now. 
Have they held or sold their stETH?


### a

Date of current balance: 2022-06-11
We got a dataset of all addresses that staked ETH someday (more than 1k usd).
We won't see how well did those that sold all their stETH (we didn't get date of sell) but we can yet see those who still have some stETH.
We'll also see how well or bad are doing those who didn't sell.


```{r}
renderDT({
  datatable(history,
    rownames = FALSE, options = list(pageLength = 5)
  )
})
```


### a

a


```{r}
renderDT({
  datatable(actions,
    rownames = FALSE, options = list(pageLength = 5)
  )
})
```


### a

a


```{r}
renderPlotly({
plot_ly(balances, x = ~USER_ADDRESS, y = ~LDO, type = 'bar') %>%
  layout(title = "",
         yaxis = list(title = "May 2022 LDO Balance" ,
                      zeroline = FALSE),
         xaxis = list(showticklabels = FALSE))
})
```


### Conclusion

a 


### References

https://etherscan.io/token/0xae7ab96520de3a18e5e111b5eaab095312d7fe84

https://stake.lido.fi/

https://flipsidecrypto.xyz/