---
title: "Avalanche Block and Transaction Performance
"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: https://github.com/manuelgirbal/flipside/tree/main/06.2022%20-%20Avalanche%20Block%20and%20Transaction%20Performance
runtime: shiny
---
<style>
body {
text-align: justify}
</style>

```{r setup, include=FALSE}
library(flexdashboard)
library(httr)
library(jsonlite)
library(tidyverse)
library(lubridate)
library(shiny)
library(plotly)
library(DT)
library(rsconnect)
```

```{r data, include=FALSE}
options(scipen=999)

data_1 <- GET("https://node-api.flipsidecrypto.com/api/v2/queries/898b643f-c654-4e0c-8007-2a07aaadc4de/data/latest")
data_2 <- GET("https://node-api.flipsidecrypto.com/api/v2/queries/2bc0867d-d760-49d6-8c35-b5f4fd2c6dd4/data/latest")
data_3 <- GET("https://node-api.flipsidecrypto.com/api/v2/queries/bc15220d-d653-4025-8003-c98dd281f111/data/latest")

data2_1 <- rawToChar(data_1$content)
data2_2 <- rawToChar(data_2$content)
data2_3 <- rawToChar(data_3$content)

data3_1 <- as_tibble(fromJSON(data2_1, flatten = TRUE))
data3_2 <- as_tibble(fromJSON(data2_2, flatten = TRUE))
data3_3 <- as_tibble(fromJSON(data2_3, flatten = TRUE))

data3_1$DATE <- as_date(data3_1$DATE)
data3_3$DATE <- as_date(data3_3$DATE)

data3_1 <- data3_1 %>% 
  mutate(DATE_HOUR = as.POSIXct(paste(data3_1$DATE, data3_1$HOUR), format="%Y-%m-%d %H"))

data3_3 <- data3_3 %>% 
  mutate(DATE_HOUR = as.POSIXct(paste(data3_3$DATE, data3_3$HOUR), format="%Y-%m-%d %H"))

```


Sidebar {.sidebar}
=======================================================================

### Description

In this dashboard, we'll explore Avalanche data and dig into the blockchain's performance at a high level. Avalanche supports quick block finality and high TPS, so we'll see this in block and transaction performance since 2022/06/20.

What this dashboard displays:

* Average number of transactions per block

* Max and min number of transactions we've seen in a block

* Transaction gas price over time (to properly measure it in AVAX this has to be divided by 1000000000)

* Average transactions per second by hour

* Average time between blocks over time

* Average transaction fees

* Average AVAX amount transacted

Data queried from:
https://flipsidecrypto.xyz

Author: manuel_g_g


Dashboard
=======================================================================

Row
-----------------------------------------------------------------------

### A {.value-box}

```{r}
renderValueBox({
  valueBox(data3_2$AVG_TX, "AVG number of transactions per block", color = "blue")
})
```

### B {.value-box}

```{r}
renderValueBox({
  valueBox(data3_2$MAX_TX, "MAX number of transactions in a block", color = "navy")
})
```

### C {.value-box}

```{r}
renderValueBox({
  valueBox(data3_2$MIN_TX, "MIN number of transactions in a block", color = "teal")
})
```

Row
-----------------------------------------------------------------------

### Transaction gas price over time

```{r}
renderPlot({
  data3_1 %>% 
  ggplot(aes(DATE_HOUR, AVG_GAS_PRICE)) +
  geom_line(size=1, color = "#00AFBB") +
  scale_x_datetime(date_breaks = "1 day", date_minor_breaks = "1 hour", date_labels = "%d-%b")
})
```

### AVG transactions per second by hour

```{r}
renderPlot({
  data3_1 %>% 
  ggplot(aes(DATE_HOUR, TPS)) +
  geom_line(size=1, color = "steelblue") +
  scale_x_datetime(date_breaks = "1 day", date_minor_breaks = "1 hour", date_labels = "%d-%b")
})
```



### AVG seconds between blocks (hourly grouped) 

```{r}
renderPlot({
  data3_3 %>% 
  ggplot(aes(DATE_HOUR, AVG_DIFFERENCE_IN_SECONDS)) +
  geom_line(size=1, color = "#009E73") +
  scale_x_datetime(date_breaks = "1 day", date_minor_breaks = "1 hour", date_labels = "%d-%b")
})
```

Row
-----------------------------------------------------------------------

### AVG transaction fees (in AVAX)

```{r}
renderPlot({
  data3_1 %>% 
  ggplot(aes(DATE_HOUR, AVG_TX_FEE)) +
  geom_line(size=1, color = "#D55E00") +
  scale_x_datetime(date_breaks = "1 day", date_minor_breaks = "1 hour", date_labels = "%d-%b")
})
```



### AVG AVAX value transacted

```{r}
renderPlot({
  data3_1 %>% 
  ggplot(aes(DATE_HOUR, AVG_AVAX_VALUE)) +
  geom_line(size=1, color = "#E69F00") +
  scale_x_datetime(date_breaks = "1 day", date_minor_breaks = "1 hour", date_labels = "%d-%b")
})
```




