---
title: "Hop Whales"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical layout: fill
    source_code: https://github.com/manuelgirbal/flipside/tree/main/06.2022%20-%20Hop%20Whales
runtime: shiny
---
<style>
body {
text-align: justify}
</style>

```{r setup, include=FALSE}
library(flexdashboard)
library(httr)
library(jsonlite)
library(tidyverse)
library(lubridate)
library(shiny)
library(plotly)
library(DT)
library(rsconnect)
```

```{r data, include=FALSE}
options(scipen=999)

data_Hop <- GET("https://node-api.flipsidecrypto.com/api/v2/queries/a3b95431-4c5b-4ae7-b8d6-88a713cc76bb/data/latest")
data_L2 <- GET("https://node-api.flipsidecrypto.com/api/v2/queries/474b623d-f32c-4162-91df-af773cf24cae/data/latest")

data2_Hop <- rawToChar(data_Hop$content)
data2_L2 <- rawToChar(data_L2$content)

data3_Hop <- as_tibble(fromJSON(data2_Hop, flatten = TRUE))
data3_L2 <- as_tibble(fromJSON(data2_L2, flatten = TRUE))

data3_Hop$DATE <- as_date(data3_Hop$DATE)
data3_L2$DATE <- as_date(data3_L2$DATE)

data3_Hop <- data3_Hop %>% 
  mutate(BRIDGE = 'Hop',
         L2 = case_when(
           RECIPIENT_CHAINID == '137' ~ "polygon",
           RECIPIENT_CHAINID == '42161' ~ "arbitrum",
           TRUE ~ "optimism"
         )) %>% 
  select(DATE, SYMBOL, L2, USER_ADDRESSES, TRANSACTIONS, AVG_AMOUNT_USD, BRIDGE)

data3_L2 <- data3_L2 %>% 
  mutate(BRIDGE = 'Native')

data4 <- data3_Hop %>% 
  union_all(data3_L2)

Tokens = c("DAI", "USDT", "USDC", "MATIC", "ETH")

L2 = c("polygon", "arbitrum", "optimism")
```


Column {.sidebar data-width=200}
-----------------------------------------------------------------------
```{r}
selectInput("Token", label = "Select token:", choices = Tokens)

selectInput("L2", label = "Select L2:", choices = L2)
```


Column {data-width=300}
-----------------------------------------------------------------------
### Description

In this dashboard you can choose your L2 and token of interest and see if whales and users are choosing Hop protocol (https://hop.exchange/) to go to Ethereum L2s (Arbitrum, Optimism, Polygon) vs their native bridges.

You'll be able to see these comparisons in three different variables: unique daily users, daily transactions, and average amount moved (measured in USD value).

Data was queried from https://flipsidecrypto.xyz/


### Unique daily users

```{r}
renderPlot({
data4 %>%
  filter(SYMBOL == input$Token,
         L2 == input$L2) %>% 
  ggplot(aes(DATE, USER_ADDRESSES, color = BRIDGE)) +
  geom_line(size=1) +
  scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 week", date_labels = "%b-%Y") +
  xlab("") +
  ylab("")
})
```


Column {data-width=300}
-----------------------------------------------------------------------

### Daily transactions

```{r}
renderPlot({
data4 %>%
  filter(SYMBOL == input$Token,
         L2 == input$L2) %>% 
  ggplot(aes(DATE, TRANSACTIONS, color = BRIDGE)) +
  geom_line(size=1) +
  scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 week", date_labels = "%b-%Y") +
  xlab("") +
  ylab("")
})
```



### Avg amount (USD value)

```{r}
renderPlot({
data4 %>%
  filter(SYMBOL == input$Token,
         L2 == input$L2) %>% 
  ggplot(aes(DATE, AVG_AMOUNT_USD, color = BRIDGE)) +
  geom_line(size=1) +
  scale_x_date(date_breaks = "1 month", date_minor_breaks = "1 week", date_labels = "%b-%Y") +
  xlab("") +
  ylab("")
})
```
